Clustering: A pipeline to analyse time-course gene expression data

### 2019-04-25 scripts/03_clustering.Rmd
MAINT Better scoring

# XXX is there a bug here?
# all_scores = data.frame(row.names=row.names(data))
# for(k in 1:n_clusters){
#     scores = moanin:::score_genes_centroid(data, centroids[k,])
#     all_scores[paste0("cluster_", k)] = scores
# }

# Only assign labels to X% of the genes
# max_score = quantile(moanin:::row_min(all_scores), c(percentage_genes_to_label))
# genes_to_not_consider = moanin:::row_min(all_scores) >= max_score
# labels = moanin:::row_argmin(all_scores)
# labels[genes_to_not_consider] = NA
```

@@

```{r results="hide", echo=FALSE}
# Save the clustering for the next step
kmeans_labels = as.data.frame(kmeans_clusters$clusters)
row.names(kmeans_labels) = row.names(y)
write.table(kmeans_labels,
	    ".results/clustering_labels.txt",
	    sep="\t")
```

>>>>

all_scores = data.frame(row.names=row.names(data))
for(k in 1:n_clusters){
     scores = moanin:::score_genes_centroid(data, centroids[k,])
     all_scores[paste0("cluster_", k)] = scores
}

# Only assign labels to X% of the genes
max_score = quantile(moanin:::row_min(all_scores), c(percentage_genes_to_label))
genes_to_not_consider = moanin:::row_min(all_scores) >= max_score
labels = moanin:::row_argmin(all_scores)
labels[genes_to_not_consider] = NA
```

@@

```{r results="hide", echo=FALSE}
# Save the clustering for the next step
kmeans_labels = as.data.frame(labels)
row.names(kmeans_labels) = row.names(y)
write.table(kmeans_labels,
	    ".results/clustering_labels.txt",
	    sep="\t")
```
